Constructing a universe for the setoid model

### 2020-06-29 paper.tex
Remark on separate sorts for propositions and sets.

>>>>

Yet another choice is whether to have two separate sorts, one for propositions
and one for sets (with propositions convertible to sets) or a single sort of
types (sets), with propositions given by elements of a universe of proposition,
which is a (large) type. We have chosen to present the second option to fit with
the standard notion of (unisorted) CwF. However, this has downsides: to even
talk about propositions, we need to have a notion of large types. The first
option is more symmetric: we can have parallel hierarchies for propositions and
sets.
